---
title: "Results DG"
output: html_document
---

This document presents results of running the recurring transactions model on the raw transactions in "Export Data - DG". The raw data consisted of transactions from 2007 through 2015. Since the model is required to run only over 90-day transaction history, the raw data was filtered to include only transactions between 11/14 - 02/15.

```{r, include=FALSE}
source('app_util.R')
library(rpart)
library(RWeka)
library(pander)
library(knitr)

m <- build_model()
```

### Checking Data

```{r, echo=FALSE}
data.raw <- load_data('C:/Users/akulkarni/Documents/Yodlee/Data driven app/DG/Export Data - DG.csv')
```
A summary of the transactions is shown below - 
```{r, results='asis', echo=FALSE}
pandoc.table(head(data.raw[, -5]), split.table=Inf)
```

```{r, echo=FALSE}
data.sim.df <- filter_similar(data.raw)
data.test   <- trans_predict(m, data.sim.df)
row.names(data.test) <- NULL
```

The model first filters in potentially similar transactions based on their description. It then runs a rules-based binary classifier to label these transactions as 'Valid' (recurring) or 'Invalid' (non-recurring) transactions.
```{r, results='asis', echo=FALSE}
pandoc.table(data.test[, 2:11], split.table=Inf)
```
The final list of recurring transactions -
```{r, results='asis', echo=FALSE}
data.result <- build_result(data.raw, data.test)
pandoc.table(data.result, split.table = Inf)
```
