---
title: "EJ Results"
output: html_document
---

This document presents results of running the recurring transactions model on the raw transactions in "Export Data Checking 1 - EJ".

```{r, include=FALSE}
source('app_util.R')
library(rpart)
library(RWeka)
library(pander)
library(knitr)

m <- build_model()
```

### Checking Data - 1

```{r, echo=FALSE}
data.raw <- load_data('C:/Users/akulkarni/Documents/Yodlee/Data driven app/EJ/Export Data Checking 1 - EJ.csv')
```
A summary of the transactions is shown below - 
```{r, results='asis', echo=FALSE}
pandoc.table(head(data.raw[, -5]), split.table=Inf)
```

```{r, echo=FALSE}
data.sim.df <- filter_similar(data.raw)
data.test   <- trans_predict(m, data.sim.df)
row.names(data.test) <- NULL
```

The model first filters in potentially similar transactions based on their description. It then runs a rules-based binary classifier to label these transactions as 'Valid' (recurring) or 'Invalid' (non-recurring) transactions.
```{r, results='asis', echo=FALSE}
pandoc.table(data.test[, 2:11], split.table=Inf)
```
The final list of recurring transactions -
```{r, results='asis', echo=FALSE}
data.result <- build_result(data.raw, data.test)
pandoc.table(data.result, split.table = Inf)
```

### Checking Data - 2

```{r, echo=FALSE}
data.raw <- load_data('C:/Users/akulkarni/Documents/Yodlee/Data driven app/EJ/Export Data Checking 2 - EJ.csv')
```
A summary of the transactions is shown below - 
```{r, results='asis', echo=FALSE}
pandoc.table(head(data.raw[, -5]), split.table=Inf)
```

```{r, echo=FALSE}
data.sim.df <- filter_similar(data.raw)
data.test   <- trans_predict(m, data.sim.df)
row.names(data.test) <- NULL
```

The model first filters in potentially similar transactions based on their description. It then runs a rules-based binary classifier to label these transactions as 'Valid' (recurring) or 'Invalid' (non-recurring) transactions.
```{r, results='asis', echo=FALSE}
pandoc.table(data.test[, 2:11], split.table=Inf)
```
The final list of recurring transactions -
```{r, results='asis', echo=FALSE}
data.result <- build_result(data.raw, data.test)
pandoc.table(data.result, split.table = Inf)
```

### Card Data

```{r, echo=FALSE}
data.raw <- load_data('C:/Users/akulkarni/Documents/Yodlee/Data driven app/EJ/Export Data Card - EJ.csv')
```
A summary of the transactions is shown below - 
```{r, results='asis', echo=FALSE}
pandoc.table(head(data.raw[, -5]), split.table=Inf)
```

```{r, echo=FALSE}
data.sim.df <- filter_similar(data.raw)
data.test   <- trans_predict(m, data.sim.df)
row.names(data.test) <- NULL
```

The model first filters in potentially similar transactions based on their description. It then runs a rules-based binary classifier to label these transactions as 'Valid' (recurring) or 'Invalid' (non-recurring) transactions.
```{r, results='asis', echo=FALSE}
pandoc.table(data.test[, 2:11], split.table=Inf)
```
The final list of recurring transactions -
```{r, results='asis', echo=FALSE}
data.result <- build_result(data.raw, data.test)
pandoc.table(data.result, split.table = Inf)
```
